%\newglossaryentry{}{name={}, description={}, sort={}}
\newglossaryentry{Acceleration}{name={Acceleration Strike (action)}, description={
    A strike in which a boss is forced to buy a robot
    immediately. This robot remains in control of the boss.}}

\newglossaryentry{Bank}{name={Bank (place)}, description={
    The reservoir of coins, property of no player.}}

\newglossaryentry{Boss}{name={Boss (role/card)}, description={
    The stingy blue character. [2–4 \faPeopleGroup] An automated role collecting
    the Rent, and buying robots. [5–10 \faPeopleGroup] Two human players.}}

\newglossaryentry{Class}{name={Class Betrayal (winning condition)}, description={
    [2–4 \faPeopleGroup] Any player can win individually by
    accumulating coins. [5–10 \faPeopleGroup] The Startupper can win by accumulating coins.}}

\newglossaryentry{Contract}{name={Contract (card/agreement)}, description={
    [2–4 \faPeopleGroup] Each of the enlistment options on the Contracts
    cards. [5–10 \faPeopleGroup] The agreements between bosses and workers happening
    during phase 1.}}

\newglossaryentry{Event}{name={Event (card)}, description={
    [2–4 \faPeopleGroup] During phase 2, the starting player reveals an Event card
    that can affect this/any/all players in an instantaneous or permanent fashion.}}

\newglossaryentry{Expropriation}{name={Expropriation Strike (action)}, description={
    A strike in which workers can take a robot from a
    chosen boss. [5–10 \faPeopleGroup] From a boss without the Security Guard.}}

\newglossaryentry{Holidays}{name={Holidays (action)}, description={
    [2–4 \faPeopleGroup] Workers can choose a Contract with Holidays to
    remove Stress. [5–10 \faPeopleGroup] Workers can remove Stress with Holidays if they: pay
    2 \faRubleSign; or choose the Public Work; or get it as part of a Contract offered by a boss.}}

\newglossaryentry{Luddite}{name={Luddite (role/card)}, description={
    [6–10 \faPeopleGroup] A saboteur secret role for workers. Adds an individual
    winning option, destroying 3 robots during failed strikes. Destroyed robots
    also count towards the workers' collective victory.}}

\newglossaryentry{Monopoly}{name={Monopoly (winning condition)}, description={
    [5–10 \faPeopleGroup] When a boss gets eliminated due to
    not being able to pay the Rent or cannot buy a robot after a successful Acceleration
    Strike. The winner gets determined based on the expropriated or destroyed
    robots. See the victory conditions Early ending of the game.}}

\newglossaryentry{Prolet}{name={Prolet (role/card)}, description={
    [5–10 \faPeopleGroup] A “virtual pauper” secret role for workers. Does not
    have any individual winning option. It's very focused on striking!}}

\newglossaryentry{Public}{name={Public Work (card)}, description={
    [5–10 \faPeopleGroup] During phase 1, workers can take this Contract
    instead of one offered from the bosses. There is only one such job in games with
    5–6 \faPeopleGroup, two in games with 7–8 \faPeopleGroup, and 3 in games with 9–10 \faPeopleGroup.}}

\newglossaryentry{Rent}{name={Rent (phase)}, description={
    In the Rent phase, each player pays an amount of coins. With [2–4
    \faPeopleGroup] the Rent goes to the automated boss, [5–10 \faPeopleGroup] The Rent goes to the Bank.}}

\newglossaryentry{Sabotage}{name={Sabotage (action)}, description={
    [6–10 \faPeopleGroup] In phase 2 Strike, the Luddite player can destroy a
    robot during a failed strike.}}

\newglossaryentry{Scab}{name={Scab (role/card)}, description={
    [5–10 \faPeopleGroup] A workaholic secret role for workers. Adds an individual
    winning option: each Scab can win together with a victory-declaring boss
    (a boss winning either with coins accumulation or Monopoly) if they were working
    (not on strike) for this boss when the victory declaration happens.}}

\newglossaryentry{Security}{name={Security Guard (card)}, description={
    [5–10 \faPeopleGroup] It is a protection from Expropriation Strike and
    Sabotage. The bosses bid for getting it (from 0 to 5 fingers, check phase 2 rules).}}

\newglossaryentry{Startupper}{name={Startupper (role/card)}, description={
    [5–10 \faPeopleGroup] A petite bourgeoisie secret role for workers.
    Adds a Class Betrayal individual winning option via the accumulation of coins
    and stealing from the Union Fund.}}

\newglossaryentry{Stress}{name={Stress (status)}, description={
    A condition for workers that hinders them from striking, and thus
    forces them to work.}}

\newglossaryentry{Tap}{name={Tap/Untap (action)}, description={
    Tap your character card, placing it rotated 90° in front of
    you for indicating Stress. Untap placing it straight.}}

\newglossaryentry{Union}{name={Union Fund (card)}, description={
    [5–10 \faPeopleGroup] The workers can share their coins, placing them on
    this card during phase 6.}}