    %
    % If you are looking for the PDF file, you can compile the .tex file or donwload the PDF from here:
    % https://github.com/ilario/The_Fully_Automated_Board_Game-LaTeX
    
    % Instruction for compiling: install TeXlive or whatever other LaTeX distribution
    %
    % pdflatex The_Fully_Automated_Board_Game-ENG
    % makeglossaries The_Fully_Automated_Board_Game-ENG
    % pdflatex The_Fully_Automated_Board_Game-ENG
    % pdflatex The_Fully_Automated_Board_Game-ENG
    
    % In order to decrease the dimension of the PDF file and reduce the resolution of some raster images, use:
    % gs -sDEVICE=pdfwrite -dPDFSETTINGS=/prepress -dPrinted=false -dNOPAUSE -dQUIET -dBATCH -dAutoFilterColorImages=false -dColorImageFilter=/FlateEncode -sOutputFile=The_Fully_Automated_Board_Game-ENG-printer_quality.pdf The_Fully_Automated_Board_Game-ENG.pdf
    % instead of preprint, you can also try /screen and /ebook

% Some rights are reserved as specified by
% Creative Commons Attribution - NonCommercial - NoDerivs version 3.0 licence
% which can be accessed on https://creativecommons.org/licenses/by-nc-nd/3.0/

\documentclass[a5paper, 10pt, openany]{book}

\usepackage[
    paperheight=17cm,
    paperwidth=14cm,
    top=1.3cm,
    bottom=1.3cm,
    heightrounded,
    %bindingoffset=1cm, % this is useful for keeping text away from the stapled union of the pages
    centering,
    marginparwidth=1.3cm,
    textwidth=11cm,
    marginparsep=0.1cm,
    %showframe
]{geometry}% booklets of the original box are 14x17 cm, perfectly filling the internal size of the box

\usepackage[T1]{fontenc}

\usepackage{fontawesome7} % for the rubles symbol with \faRubleSign and for the busts symbol with \faPeopleGroup

\usepackage[english]{babel}% spanish, italian, catalan, 

\usepackage{hyperref}
    \hypersetup{
        hidelinks,
        pdftitle={The Fully Automated Board Game - English rulebook},
    %        pdfsubject={Your PDF subject},
        pdfauthor={No Board Games}
        pdfkeywords={the fully automated board game, no boad games} % list of keywords
    }
    
% allowing url breaks at hyphens https://tex.stackexchange.com/a/3034/173645
% https://tex.stackexchange.com/a/407368/173645
\usepackage{xurl}

\usepackage{xcolor} % for colors in hyperref links and in thumbs
    \definecolor{colorone}{HTML}{1B9E77}
    \definecolor{colortwo}{HTML}{d95f02}
%    \definecolor{colorthree}{HTML}{7570B3}
%    \definecolor{colorfour}{HTML}{E7298A}
%    \definecolor{colorfive}{HTML}{66A61E}
%    \definecolor{colorsix}{HTML}{E6AB02}
%    \definecolor{colorseven}{HTML}{A6761D}
%    \definecolor{coloreight}{HTML}{666666}

\usepackage{glossaries} % list of explained concepts at the end of the rulebook
    \makeglossaries % has to be after glossaries and after hyperref
    \setacronymstyle{long-sp-short}

% automagically reduces overfull lines and improves justification, but the compilation takes longer
\usepackage{microtype} 

% for customizing titles
\usepackage{titlesec}
    % for removing "Chapter 1" from the first chapter's page
    % taken from https://tex.stackexchange.com/a/120743/173645
    \titleformat{\chapter}[display]{\normalfont\bfseries}{}{0pt}{\Huge}

% to add a subtitle. Taken from here: https://apurbapaul.blogspot.com/2013/01/subtitle-in-latex.html
\usepackage{titling}
    \newcommand{\subtitle}[1]{%
        \posttitle{%
            \par\end{center}
        \begin{center}\large#1\end{center}
        \vskip0.1em}}%
    
    % bigger main title
    \pretitle{\begin{center}\Huge}
    \posttitle{\par\end{center}\vskip 0.5em}

% to add the colorful marks on the page edges
\usepackage[width=1cm]{thumbs}

% electronic pdf bookmark, no change in the printed version
\usepackage{bookmark}

\usepackage{epigraph}% for inserting stupid phrases in random places
%\setlength{\epigraphrule}{0pt}% eliminate the rule below the epigraphs
    
\usepackage{rotating} % for vertical sideways text


% limit main table of content to sections, do not print subsections
\setcounter{tocdepth}{1}

% we don't want to show the 1.2.3 numbering before the section titles, but we still want them to appear in the table of contents
% using \section*{} removes the numbering but also removes them from the ToC
% solution taken from https://tex.stackexchange.com/a/11669/173645
\setcounter{secnumdepth}{0}


\title{\uppercase{The Fully Automated\\ Boardgame}\\
    English rulebook}

\subtitle{A party game about robots and strikes.\\
    Become a greedy boss or a riotous worker!
    
    ---
    
    From 2 to 10 players\\
    Duration 1 to 60 minutes}
\author{No Board Games}
\date{2025}


\begin{document}

\selectlanguage{english}

\maketitle

\tableofcontents



\mainmatter

\input{contents_tex/preamble.tex}

\chapter{Rules for 5 to 10 players}\label{ch:5-10}

    \addthumb{\thechapter}{\begin{sideways}\large{\textbf{5-10 \faPeopleGroup}}\end{sideways}}{white}{colorone}

    \input{contents_tex/five_to_ten_players.tex}

    \stopthumb
    
    \clearpage

\chapter{Rules for 2 to 4 players}\label{ch:2-4}

    \addthumb{\thechapter}{\begin{sideways}\large{\textbf{2-4 \faPeopleGroup}}\end{sideways}}{white}{colortwo}

    \graphicspath{ {./contents_img/} }

    \input{contents_tex/two_to_four_players.tex}

    \stopthumb

\appendix
    
    %%%%%%%%%%%%
    % GLOSSARY %
    %%%%%%%%%%%%

%\newglossaryentry{}{name={}, description={}, sort={}}
\newglossaryentry{Acceleration}{name={Acceleration Strike (action)}, description={
    A strike in which a boss is forced to buy a robot
    immediately. This robot remains in control of the boss.}}
\newglossaryentry{Bank}{name={Bank (place)}, description={
    The reservoir of coins, property of no player.}}
\newglossaryentry{Boss}{name={Boss (role/card)}, description={
    The stingy blue character. [2–4 \faPeopleGroup] An automated role collecting
    the Rent, and buying robots. [5–10 \faPeopleGroup] Two human players.}}
\newglossaryentry{Class}{name={Class Betrayal (winning condition)}, description={
    [2–4 \faPeopleGroup] Any player can win individually by
    accumulating coins. [5–10 \faPeopleGroup] The Startupper can win by accumulating coins.}}
\newglossaryentry{Contract}{name={Contract (card/agreement)}, description={
    [2–4 \faPeopleGroup] Each of the enlistment options on the Contracts
    cards. [5–10 \faPeopleGroup] The agreements between bosses and workers happening
    during phase 1.}}
\newglossaryentry{Event}{name={Event (card)}, description={
    [2–4 \faPeopleGroup] During phase 2, the starting player reveals an Event card
    that can affect this/any/all players in an instantaneous or permanent fashion.}}
\newglossaryentry{Expropriation}{name={Expropriation Strike (action)}, description={
    A strike in which workers can take a robot from a
    chosen boss. [5–10 \faPeopleGroup] From a boss without the Security Guard.}}
\newglossaryentry{Holidays}{name={Holidays (action)}, description={
    [2–4 \faPeopleGroup] Workers can choose a Contract with Holidays to
    remove Stress. [5–10 \faPeopleGroup] Workers can remove Stress with Holidays if they: pay
    2 \faRubleSign; or choose the Public Work; or get it as part of a Contract offered by a boss.}}
\newglossaryentry{Luddite}{name={Luddite (role/card)}, description={
    [6–10 \faPeopleGroup] A saboteur secret role for workers. Adds an individual
    winning option, destroying 3 robots during failed strikes. Destroyed robots
    also count towards the workers' collective victory.}}
\newglossaryentry{Monopoly}{name={Monopoly (winning condition)}, description={
    [5–10 \faPeopleGroup] When a boss gets eliminated due to
    not being able to pay the Rent or cannot buy a robot after a successful Acceleration
    Strike. The winner gets determined based on the expropriated or destroyed
    robots. See the victory conditions Early ending of the game.}}
\newglossaryentry{Prolet}{name={Prolet (role/card)}, description={
    [5–10 \faPeopleGroup] A “virtual pauper” secret role for workers. Does not
    have any individual winning option. It's very focused on striking!}}
\newglossaryentry{Public}{name={Public Work (card)}, description={
    [5–10 \faPeopleGroup] During phase 1, workers can take this Contract
    instead of one offered from the bosses. There is only one such job in games with
    5–6 \faPeopleGroup, two in games with 7–8 \faPeopleGroup, and 3 in games with 9–10 \faPeopleGroup.}}
\newglossaryentry{Rent}{name={Rent (phase)}, description={
    In the Rent phase, each player pays an amount of coins. With [2–4
    \faPeopleGroup] the Rent goes to the automated boss, [5–10 \faPeopleGroup] The Rent goes to the Bank.}}
\newglossaryentry{Sabotage}{name={Sabotage (action)}, description={
    [6–10 \faPeopleGroup] In phase 2 Strike, the Luddite player can destroy a
    robot during a failed strike.}}
\newglossaryentry{Scab}{name={Scab (role/card)}, description={
    [5–10 \faPeopleGroup] A workaholic secret role for workers. Adds an individual
    winning option: each Scab can win together with a victory-declaring boss
    (a boss winning either with coins accumulation or Monopoly) if they were working
    (not on strike) for this boss when the victory declaration happens.}}
\newglossaryentry{Security}{name={Security Guard (card)}, description={
    [5–10 \faPeopleGroup] It is a protection from Expropriation Strike and
    Sabotage. The bosses bid for getting it (from 0 to 5 fingers, check phase 2 rules).}}
\newglossaryentry{Startupper}{name={Startupper (role/card)}, description={
    [5–10 \faPeopleGroup] A petite bourgeoisie secret role for workers.
    Adds a Class Betrayal individual winning option via the accumulation of coins
    and stealing from the Union Fund.}}
\newglossaryentry{Stress}{name={Stress (status)}, description={
    A condition for workers that hinders them from striking, and thus
    forces them to work.}}
\newglossaryentry{Tap}{name={Tap/Untap (action)}, description={
    Tap your character card, placing it rotated 90° in front of
    you for indicating Stress. Untap placing it straight.}}
\newglossaryentry{Union}{name={Union Fund (card)}, description={
    [5–10 \faPeopleGroup] The workers can share their coins, placing them on
    this card during phase 6.}}


% glossary
\glsaddall
\printglossary

\end{document}
